\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}

\hypersetup{
    colorlinks,%
    citecolor=blue,%
    filecolor=blue,%
    linkcolor=blue,%
    urlcolor=blue 
    %urlcolor=mygreylink     % can put red here to better visualize the links
}

\author[Sowmya Vajjala]{Instructor: Sowmya Vajjala}

\title[LING 520]{LING 520: Computational Analysis of English}
\subtitle{Semester: FALL '16}

\date{25 October 2016}

\institute{Iowa State University, USA}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frame}\titlepage
\end{frame}

\begin{frame}
\frametitle{Class Outline}
\begin{itemize}
\item Discussion about last week's text classification exercise
\item General review
\item Natural Language Parsing - introduction
%\item Phrase structure parsing
%\item Dependency parsing
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Announcements, Reminders etc}
\begin{itemize}
\item Assignment 4 is due on saturday.
\item My code examples from friday's tutorial: I uploaded what I already discussed. Please go through the code, AND the comments.
\item I will continue with doing some review today.
\item All Coursera courses and lectures I mentioned about in this class are free. If anyone is unable to download the content, take a copy from me.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{General comments on the Delta part of the feedback}
the 'What needs to change in the course' part:
\begin{itemize}
\item More in-class (directed) practice needed (almost everyone) \pause
\item More assignments (yes, one person wants it) - problem sets are there for a reason! \pause
\item More review classes (2) - Will do, but not extra classes. \pause
\item More code samples sharing, annotated code etc (2) - this is in your hands. \pause
\item More of 'dissecting the code' (1) - not really done in a classroom, but will do today. \pause
\item course is too fast, accept the bitter fact that different students have different learning curves etc. (2) - I already accepted some 27 years ago when I enrolled in school :) \pause
\item More doing less lecturing (1) - I do not know how anyone can do anything in this topic without the 'lecture' part.  \pause
\item Time for doing graded assignments in class (1) - Not possible. This is a graduate class. \pause
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{General comments on the Delta part of the feedback}
the 'What I need to change' part:
\begin{itemize}
\item do more practice (almost everyone)
\item do more review (2-3)
\item more communication with instructor (1-2)
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Discussion about last week's exercise}
\begin{itemize}
\item Last Thursday, I asked you to pick one of the text classification examples from NLTK book and work through them to understand what is happening.
\item I want each team to briefly summarize what they did, how much they understood in the process etc.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{}
\Large General Review
\end{frame}

\begin{frame} %paavu ganta
\frametitle{Reading a saved dictionary}
\begin{itemize}
\item Question: How do you store a dictionary on to your hard disk? How will you access this dictionary in another program? How many people successfully did this? How?\pause
\item Here is one way of doing it: dictionary-creation.py, dictionary-use.py
\end{itemize}
\end{frame}

\begin{frame} %araganta
\frametitle{Probability and Programming}
\begin{itemize}
\item Katrin Erk's code, line by line + more.
\item Note: This is the best and most comprehensible code on this topic I found so far. You are more than welcome to find something easier than this and share with the class if you think I am wasting your time by repeatedly talking about this. 
\end{itemize}
%Go through the code line by line.
\end{frame}

\end{document}





