\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{relsize}

\hypersetup{
    colorlinks,%
    citecolor=blue,%
    filecolor=blue,%
    linkcolor=blue,%
    urlcolor=blue 
    %urlcolor=mygreylink     % can put red here to better visualize the links
}

\author[Sowmya Vajjala]{Instructor: Sowmya Vajjala}

\title[LING 520]{LING 520: Computational Analysis of English}
\subtitle{Semester: FALL '16}

\date{6 October 2016}

\institute{Iowa State University, USA}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frame}\titlepage
\end{frame}

\begin{frame}
\frametitle{Class outline}
\begin{itemize}
\item Revision of what we discussed so far
\item Discussion about final projects
\item Planning for the tutorial session
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Topics discussed so far}
\begin{enumerate}
\item Regular expressions
\item Pre-processing of text: tokenizing, sentence splitting
\item Text normalization, morphology: spelling correction, stemming, lemmatization
\item Language models, evaluating them, building and using them
\item POS tagging
\end{enumerate}
 ... +3 assignments.
\end{frame}

\begin{frame}
\frametitle{Topics for the coming weeks}
\begin{enumerate}
\item Text classification (most useful in my opinion)
\item Parsing sentences
\item Other topics: Discourse, Semantic analysis etc.
\item NLP Applications (quick overview)
\item NLP for CALL
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Specific Issues}
\begin{itemize}
\item What has been difficult so far conceptually, apart from mathematical notation? \pause
\item What has been difficult in terms of writing python code? \pause
\item Is there sufficient time to do the assignments? \pause
\item What specific topics would you want me to revise in an extra class? \pause
\item What specific programming practice do you want?
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Some questions}
\begin{itemize}
\item How many of you regularly follow NLTK book examples on topics discussed in the class? \pause
\item Do you refer to any other sources beyond classroom slides and NLTK? \pause
\item How many of you actually write some programs for their dissertation work or RA work? \pause
\item How many of you still are considering writing some programs to use in your dissertation work? \pause
\item Do you think you have a picture of what kind of problems one faces in writing code for text processing? \pause
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Planning for a Tutorial Session}
\begin{enumerate}
\item Any day after 17th October: Thursday or Friday evening, after 5pm
\item Weekends: Saturday will work, provided I am in town
\item What will happen: some amount of discussion and lot of group work, or the other way round?
\item Topics: let us decide before hand via a wishlist. 
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{About Final projects}
\begin{itemize}
\item Some example ideas are uploaded on BB. You can come up with your own ideas, but get them approved by me.
\item Carries 20 marks. 10 marks for written reports, and a oral defense. 10 marks for the actual implementation.
\item Initial report describing your idea and plan: Due on 5th November.
\item Final submission due: 9 December. 
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Ideas}
\begin{itemize}
\item Ideas on BB
\item Anyone who already know what they want to do can mention it.
\item Others without that clarity yet: Decide before we finish text classification. We will discuss this again in 2 weeks!
\end{itemize}
\end{frame}

%Exercise 5.2--5.4 from J&M
\begin{frame}
\frametitle{Pen and paper exercise}
\framesubtitle{Exercises 5.2--5.4 in J\&M}
\begin{itemize}
\item Using the tags from PTB and CLAWS7 tagsets, tag the following sentences manually, ignoring the punctuation. Compare your tags with your neighbors to discuss the agreement.
\item Sentences: (you can also compare yourself to Stanford POS tagger, for example)
\begin{enumerate}
\item It is a nice night.
\item This crap game is over a garage in Fifty-second Street...
\item ...Nobody ever takes the newspapers she sells...
\item He is a tall, skinny guy with a long, sad, mean-looking kisser, and a mournful voice.
\item ... I am sitting in Mindy's restaurant putting on the gefillte fish, which is a dish I am very fond of ...
\item When a guy and a doll get to talking pecks back and forth at each other, why there you are indeed. 
\end{enumerate}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Next Class}
\begin{itemize}
\item Text Classification - Introduction
\item Please read: Chapter 5 in Language and Computers. Get hold of atleast this chapter from someone in the class who has the book. No other book introduces text classification in such light weight language.
\item Video: 10.4 in Radev's course. 25min video. 
\item For practical stuff: Chapter 6 in NLTK
\end{itemize}
\end{frame}


\end{document}



